---
title: "RLohiya_Assignment9"
author: "Ritesh Lohiya"
date: "October 26, 2018"
output: html_document
---

#                             ASSIGNMENT 9

#           IS 605 FUNDAMENTALS OF COMPUTATIONAL MATHEMATICS

#                  CHAPTER 9. CENTRAL LIMIT THEOREM

PS1. The price of one share of stock in the Pilsdorff Beer Company (see Exercise 8.2.12) is given by $Y_n$ on the nth day of the year. Finn observes that the differences $X_n = Y_{n+1} - Y_n$ appear to be independent random variables with a common distribution having mean µ = 0 and variance $\sigma^2 = 1/4$. If $Y_1 = 100$, estimate the probability that $Y_{365}$ is

(a) $Y_{365}$  $\ge 100$.

```{r}
pnorm(100-100, mean = 0, sd = sqrt(364/4), lower.tail = F)
```

(b) $Y_{365}$ $\ge 100$.

```{r}
pnorm(110-100, mean = 0, sd = sqrt(364/4), lower.tail = F)
```

(c) $Y_{365}$ $\ge 100$

```{r}
pnorm(120-100, mean = 0, sd = sqrt(364/4), lower.tail = F)
```





PS2: Calculate the expected value and variance of the binomial distribution using the moment generating function.



The moment generating function: 

$M(t)=[(1-p) +pe^t]^n$.

$M'(t) = n(pe^t)[(1-p)+pe^t]^{n-1}$

Expected value: $M'(0) = np$

$M''(t) = n(n-p)(pe^t)^2[(1-p)+pet]^{n-2} + n(pe^t)[(1-p)+pe^t]^{n-1}$

Variance: $M''(0) = n(n-1)p^2 + np$

$\sigma^2 = M''(0) - [M'(0)]^2 = np(1-p)$






PS3: Calculate the expected value and variance of the exponential distribution using the moment generating function.

$M(t) = \frac{\lambda}{\lambda-t}$

$M'(t) = \frac{\lambda}{(\lambda-t)^2}$

Expected Value: $M'(0) = 1/{\lambda}$

$M''(t) = \frac{2\lambda}{(\lambda-t)^3}$

$M''(0) = \frac2{(\lambda)^2}$

$\sigma^2 = \frac2{(\lambda)^2} - (1/{\lambda})^2 = (1/{\lambda})^2$










